---
title: |
       | Error handling in R with tryCatchLog:
       | Catching, logging, post-mortem analysis
author: Jürgen Altfeld
date:   April 2018</br></br></br><p style="font-size:0.5em">These slides have been created with RMarkdown and the package <a href="https://github.com/rstudio/revealjs">revealjs</a><p>
description: Introduction into basic condition handling with R
             and advanced condition handling with the package tryCatchLog
output:
        revealjs::revealjs_presentation:
          mathjax: null
# Avoid loading mathjax from the internet
# See also: https://rmarkdown.rstudio.com/revealjs_presentation_format.html
          self_contained: true
#          self_contained: false
# chalkboard added Nov. 2016: https://github.com/rstudio/revealjs/issues/42 but this requires "selfcontained" = false !!!
#          reveal_plugins: ["notes", "search", "zoom", "chalkboard"]
          theme: white
          highlight: tango
          center: false
          height: 1024
          width: 1920
          margin: 0.1
          minScale: 0.2
          maxScale: 1.0
          reveal_options:
            slideNumber: true
#            previewLinks: true
#
# Child Rmd files are currently not supported as vignettes in R so I had to rename
# the file endings from "Rmd" to "Rmd_child" as workaround until the R issue is solved and released.
# See:
# https://github.com/yihui/knitr/issues/1540
# https://bugs.r-project.org/bugzilla3/show_bug.cgi?id=17416
vignette: >
  %\VignetteIndexEntry{Error handling in R with tryCatchLog}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r child = "tryCatchLog/vignettes/01_license.Rmd_child"}
```



<!-- !!! NEVER EVER ADD HTML COMMENTS INSIDE OF THE STYLE TAG SINCE IT BREAKS THE STYLE SOMETIMES !!! -->

<style type="text/css">

  .reveal .slides .title {
    font-size: 125%;
    margin-bottom: 150px;
    color: black;
    text-transform: none;
  }

  .reveal .slides .author {
    font-size: 75%;
    color: grey;
    text-transform: none;
  }

  .reveal .slides .date {
    font-size: 75%;
    color: grey;
    text-transform: none;
  }

  .reveal .slide h1 {
    font-size: 40px;
    text-align: left;
    color: blue;
    text-transform: none;
  }

  .reveal .slide h2 {
    font-size: 30px;
    text-align: left;
    color: blue;
  }

  .reveal .slide h3 {
    font-size: 20px;
    text-align: left;
    color: blue;
  }


  .reveal section > p {
    text-align: left;
    font-size: 70%;
  }

  .reveal section ul  {
    list-style-type: square;
    display: block;
    font-size: 70%;
  }

  .reveal section ol  {
    display: block;
    font-size: 70%;
  }
  
  .reveal section code {
    font-size: 90%;
    font-familie: Courier
  }

  .reveal pre {
    width: 98%;
  }

</style>


```{r child = "tryCatchLog/vignettes/05_overview.Rmd_child"}
```



```{r child = "tryCatchLog/vignettes/02_toc.Rmd_child"}
```

[Printable version of these slides](?print-pdf)



```{r child = "03_keyboard_shortcuts.Rmd"}
```



```{r child = "tryCatchLog/vignettes/10_standard_R_conditions.Rmd_child"}
```



```{r child = "tryCatchLog/vignettes/20_tryCatchLog.Rmd_child"}
```



```{r child = "tryCatchLog/vignettes/90_appendix.Rmd_child"}
```


